%-------------------------
% Resume in Latex
% Author : Krishna Kumar
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear header/footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting with extra space after
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{2pt}]

\pdfgentounicode=1

%-------------------------------------------
%%%%%%  CUSTOM COMMANDS FOR BULLETS  %%%%%%%
% Single resume item (bullet)
\newcommand{\resumeItem}[1]{\item \small{#1 \vspace{-2pt}}}

% Subheading for job/project/role WITHOUT bullet, aligned properly
\newcommand{\resumeSubheading}[4]{%
  \vspace{-2pt}
  \noindent
  \textbf{#1} \hfill \textit{\small #2} \\ % Company name and dates
  \textit{\small #4 | #3} \vspace{-2pt}  % Role and location
  \vspace{2pt}
}

% Optional sub-item (nested bullet)
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% List environment for job/project sections
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.2in, label=\textbullet]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% List environment for plain bullet points
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in, label=\textbullet]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% List environment for summary (no bullet)
\newcommand{\resumeSummaryListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSummaryListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Krishna Kumar} \\ \vspace{1pt}
    \small Noida, India $|$ +91 8933038005 $|$ 
    \href{mailto:krishnakum@gmail.com}{krishnakumar.myjobs@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/krishna-kumar2021/}{linkedin.com/in/krishna-kumar2021/}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSummaryListStart
\item \textbf{Data Engineer} with \textbf{7+ years} of experience designing, building, and optimizing \textbf{scalable data pipelines} and platforms. Expert in \textbf{ETL/ELT}, \textbf{data warehousing}, and \textbf{cloud solutions (GCP)}, with hands-on experience in \textbf{SQL}, \textbf{Python}, \textbf{Spark}, and \textbf{Hadoop}.
\item Proven ability to enable analytics, reporting, and ML workflows by building reliable, high-quality data foundations. Collaborative and open to exploring \textbf{ML/AI-driven data solutions}.
\resumeSummaryListEnd
\vspace{3mm}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItemListStart
\resumeItem{\textbf{Languages:} Python, SQL, Java}
\resumeItem{\textbf{Cloud / GCP:} BigQuery, Dataflow (Apache Beam), Pub/Sub, DataProc, Cloud Functions, Cloud Composer, GCS, BigTable, Data Fusion, Cloud SQL, Cloud Scheduler, Airflow}
\resumeItem{\textbf{Big Data:} Apache Spark, Hadoop, HDFS, Kafka}
\resumeItem{\textbf{BI Tools:} Tableau, Power BI}
\resumeItem{\textbf{AWS:} EC2, S3, RDS}
\resumeItem{\textbf{Database:} MySQL / RDBMS}
\resumeItem{\textbf{Version Control:} Docker, Kubernetes}
\resumeItem{\textbf{Version Control:} GitHub, Azure DevOps}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{3mm}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

% HCL Tech
\resumeSubheading
{HCL Tech}{Mar 2024 -- Present}{Noida, India}{Technical Lead}

% Project headings without bullets
\noindent\textbf{ Project: On-Prem to GCP Cloud Data Platform Migration (Finance Domain)}
\resumeItemListStart
\resumeItem{Led full migration of enterprise data pipelines from on-prem to GCP, improving system scalability by 40\% and operational efficiency by 35\%.}
\resumeItem{Designed and implemented batch and streaming pipelines to process over 10 TB of financial and transactional data daily.}
\resumeItem{Built and optimized BigQuery data models for analytics, reporting, and downstream consumption, reducing query runtime by 30\%.}
\resumeItem{Developed robust ETL/ELT workflows with automated data quality checks, monitoring, and failure-handling frameworks.}
\resumeItem{Partnered with analytics and business teams to deliver scalable, cloud-native data solutions.}
\resumeItem{Ensured compliance with cloud security, governance, and performance best practices.}
\resumeItemListEnd

\noindent\textbf{ Project: Cloud-Based Data Pipeline Development (Finance Product)}
\resumeItemListStart
\resumeItem{Designed and developed scalable batch and streaming pipelines handling 5+ TB of transactional and event-driven data per day.}
\resumeItem{Built optimized transformations and curated datasets to support near real-time analytics, reducing pipeline latency by 25\%.}
\resumeItem{Collaborated with stakeholders to deliver high-quality, reliable data solutions enabling accurate reporting and analytics.}
\resumeItem{Applied best practices in pipeline orchestration, performance tuning, and data reliability.}
\resumeItem{Supported downstream analytics and ML workflows with clean, well-structured, and trusted data.}
\resumeItemListEnd
\vspace{2mm}

% Accenture
\resumeSubheading
{Accenture}{June 2022 -- Mar 2024}{Noida, India}{Senior Data Engineer}
\resumeItemListStart
\resumeItem{Developed batch and streaming pipelines using GCP Dataflow, Airflow, Pub/Sub, and Python to support data lake migration.}
\resumeItem{Built complex BigQuery stored procedures and ETL workflows; implemented Cloud Functions and automated DAGs deployment.}
\resumeItem{Worked closely with Business Analysts to gather requirements and deliver high-quality, production-ready pipelines.}
\resumeItem{Improved pipeline performance and reliability by 25\% through optimization and monitoring frameworks.}
\resumeItemListEnd
\vspace{2mm}

% Ericsson - Data Engineer
\resumeSubheading
{Ericsson Global India Limited}{Oct 2021 -- June 2022}{Noida, India}{Data Engineer}
\resumeItemListStart
\resumeItem{Built streaming pipelines using GCP Dataflow and processed large-scale financial and network data in BigQuery and Spark.}
\resumeItem{Managed cluster and infrastructure using DataProc; delivered KPI insights for network performance improvements.}
\resumeItemListEnd
\vspace{2mm}

% Ericsson - Data Analyst
\resumeSubheading
{Ericsson Global India Limited}{Oct 2018 -- Sep 2021}{Noida, India}{Data Analyst}
\resumeItemListStart
\resumeItem{Led Tableau dashboard development and reporting solutions for multiple telecom clients.}
\resumeItem{Processed batch data using GCP Dataflow templates and Apache Spark; built complex BigQuery views for analytics.}
\resumeItem{Performed data analysis using Python (Pandas, NumPy, Matplotlib) and automated processes, achieving 75\% time savings.}
\resumeItem{Ensured 98\% SLA compliance and collaborated with clients for business strategy improvements.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{3mm}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\noindent\textbf{Diploma in Machine Learning and AI} (University of Hyderabad) \hfill 2021 -- 2022 \\

\noindent\textbf{B. Tech, Electronics and Communication} (PSIT/AKTU) 78\% \hfill 2014 -- 2018 \\


\resumeSubHeadingListEnd
\vspace{3mm}

%-----------CERTIFICATIONS & AWARDS-----------
\section{Certifications \& Awards}
\resumeSubHeadingListStart
\resumeItemListStart
\resumeItem{GCP Associate Cloud Engineer}
\resumeItem{AWS Certified Solutions Architect} 
\resumeItem{Azure Skill Badges}
\resumeItem{Python for Data Science (IBM)} 
\resumeItem{IBM Certified Data Analyst}
\resumeItem{Machine Learning Fundamentals \& Experiences (Ericsson Managed Services)}
\resumeItem{Client Value Creation Award (Accenture); Ericsson ACE Award; Best Performer of the Month (2x); Excellent Service Delivery Award}
\resumeItem{Gold Badge for Python on HackerRank}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{3mm}

\end{document}
